A Fredholm integral equation approach to computing Stokes eigenvalues in the plane

### 2019-03-13 doc/draft-01-stokes/03analysis2.tex
updating section 3.6

In~\cite{zhao2015robust}, the authors prove that
for computing the Laplace eigenvalues on regions with 
analytic boundaries, when the integral
operators are discretized using Kress-quadratures,
the determinant of the Nystr\"{o}m discretized operators
at the true eigenvalues converge to $0$ exponentially in $N$.
Thus, is the eigenvalues have multiplicity $1$, i.e. the
derivative of the determinant is non-zero at the true-eigenvalues,
then the analyticity of the discretized determinant implies
that the zeros of the determinant of the Nystr\"{o}m 
discretization of the linear operator converges
exponentially to the true Dirichlet eigenvalues for Laplace's equation.

The proof presented in~\cite{zhao2015robust} carries forward
for computing the Dirichlet eigenvalues of Stokes equation as well.
We summarize the result in the following theorem.
\begin{thrm}
Suppose that $\Omega$ is a simply connected domain with an analytic boundary.
Let $k_{j}$, $j=1,2,\ldots M$ denote all the Dirichlet eigenvalues of Stokes
equation on $\Omega$ contained in the interval $[a,b]$. 
Suppose further that all the eigenvalues have multiplicity $1$.
Let $f^{N}(k) = \text{det}(I+M^{N}_{k})$, where $M^{N}_{k}$ 
is the Nystr\"{o}m discretzation of $-2\cD_{k} - 2\cW$ with Kress
quadratures.
Then $f^{N}(k)$ has exactly $M$ zeros on the interval $[a,b]$. 
Let $\omega_{j}$, $j=1,2\ldots M$ denote the zeros of $f^{N}$.
Furthermore, there exist constants $a>0$ and $C$, 
such that $\sup_{j=1}^{M} |\omega_{j} - k_{j}| < C e^{-aN}$.
\end{thrm}

@@

>>>>

In~\cite{zhao2015robust}, the authors prove that
for computing the Laplace eigenvalues on regions with 
analytic boundaries, when the integral
operators are discretized using Kress-quadratures~\cite{kress1991boundary},
the determinant of the Nystr\"{o}m discretized operators
at the true eigenvalues converge to $0$ exponentially in $N$.
Thus, is the eigenvalues have multiplicity $1$, i.e. the
derivative of the determinant is non-zero at the true-eigenvalues,
then the analyticity of the discretized determinant implies
that the zeros of the determinant of the Nystr\"{o}m 
discretization of the linear operator converges
exponentially to the true Dirichlet eigenvalues for Laplace's equation.

The proof presented in~\cite{zhao2015robust} carries forward
for computing the Dirichlet eigenvalues of Stokes equation as well.
We summarize the result in the following theorem.
\begin{thrm}
\label{thm:mainconvfreddet}
Suppose that $\Omega$ is a simply connected domain with an analytic boundary.
Let $k_{j}$, $j=1,2,\ldots M$ denote all the Dirichlet eigenvalues of Stokes
equation on $\Omega$ contained in the interval $[a,b]$. 
Suppose further that all the eigenvalues have multiplicity $1$.
Let $f^{N}(k) = \text{det}(I+M^{N}_{k})$, where $M^{N}_{k}$ 
is the Nystr\"{o}m discretzation of $-2\cD_{k} - 2\cW$ with Kress
quadratures.
Then $f^{N}(k)$ has exactly $M$ zeros on the interval $[a,b]$. 
Let $\omega_{j}$, $j=1,2\ldots M$ denote the zeros of $f^{N}$.
Furthermore, there exist constants $a>0$ and $C$, 
such that $\sup_{j=1}^{M} |\omega_{j} - k_{j}| < C e^{-aN}$.
\end{thrm}

@@

\begin{remark}
The same analysis does not carry through for the operator
$\cI - 2 \cD_{k} - 2i\eta \cS_{k} - 2\cW$, 
since $\cS_{k}$ is not a trace class operator.
For brevity, let $\cM_{k} = -2\cD_{k} - 2i\eta \cS_{k} - 2\cW$.
The operator $\cM_{k}$ is 
in $\cJ_{2}(\bL^{2}(\Gamma))$ where
$\cJ_{2}(\bL^{2}(\Gamma))$ is the space of Hilbert-Schmidt operators
on $\bL^{2}(\Gamma)$ (the singular values of the operator are square
summable, as opposed to being summable).
Thus the Fredholm determinant of $\cI + \cM_{k}$
is not necessarily convergent. 
However, as noted in~\cite{zhao2015robust}, the convergence
result~\cref{thm:mainconvfreddet}
should be true up to a logarithmic factor in the rate
of convergence, since the singular values of the operator
$\cM_{k}$ decay like $\frac{1}{n}$, and the
Fredholm determinant divergers logarithmically. 
Instead, in~\cref{subsec:convannulus}, we demonstrate that this fact
numerically on the annulus, where the eigenvalues are analytically known. 
\end{remark}
